\chapter{Milestones}

The project milestones have been structured to address the identified risks and challenges while ensuring progress towards the research goals within the designated time frame. Each milestone is aligned with specific goals, deliverables, and risk mitigation strategies.

The project has been organized into milestones, each broken down into weekly sprints and aligned accordingly. Every sprint is accompanied by a set sprint goal documented in GitHub issues, focusing on the milestone it corresponds to. To bolster project management, a Kanban board will be utilized to monitor task progress effectively.

\section{Scoping}

Due by February 29, 2024.\newline

\noindent\textbf{Goal:} Foundation for the project is established by conducting a thorough literature review, defining project goals, scope, and assessing potential risks. Project milestones are created with clear descriptions and goals as well as risks related to them are assessed. Necessary software for the project is identified and selected for the process with suitable permissions.\newline

\noindent\textbf{Artifacts:} Project plan, risk analysis, detailed project description, context, milestones, initial bibliography\newline

\noindent\textbf{Sprints:} 3. Weeks 5-6, 7-8, 9\newline

\section{Implementing lockstep architecture}

Due by March 20, 2024.\newline

\noindent\textbf{Goal:} Lockstep architecture is created and tested. \newline

\noindent\textbf{Artifacts:} Lockstep architecture implementation, documentation. \newline

\noindent\textbf{Sprints:} 2. Weeks 10-11, 12\newline

\section{Work on DOTS determinism}

Due by April 10, 2024.\newline

\noindent\textbf{Goal:} It's confirmed that full determinism in DOTS is achivable or summarized what is the state of it and if it's sufficient for the project. Overview of determinism in DOTS is created and all the aspects are summarized. Additionally in preparation for the next milestone prototype plan for the game will be prepared\newline

\noindent\textbf{Artifacts:} Determinism tests and implementation, detailed determinism overview, game prototype plan \newline

\noindent\textbf{Sprints:} 2. Weeks 13-14, 15\newline

\section{Game prototype}

Due by April 24, 2024.\newline

\noindent\textbf{Goal:} MVP version of the game is created with necessary functionalities and reasoning why this game will be a good example for this project. The game will also validate the previous lockstep and determinism implementations \newline

\noindent\textbf{Artifacts:} Game prototype, documentation\newline

\noindent\textbf{Sprints:} 1. Weeks 16-17\newline

\section{Integrating GGPO}

Due by June 12, 2024.\newline

\noindent\textbf{Goal:} GGPO is integrated (or a custom implementation is created) with the game prototype built on Unity's DOTS framework. Client prediction is implemented, which consist of: game-state copying, rollback, and resimulation.\newline

\noindent\textbf{Artifacts:} GGPO structure integrated in the game, documentation. \newline

\noindent\textbf{Sprints:} 4. Weeks 18-19, 20-21, 22-23, 24\newline

\section{Testing and evaluating the results}

Due by June 19, 2024.\newline

\noindent\textbf{Goal:} Testing of the game prototype with multiple entities and players with different network conditions is conducted and results are evaluated based on previous assumptions. \newline

\noindent\textbf{Artifacts:} Test results and evaluation analysis. \newline

\noindent\textbf{Sprints:} 1. Week 25\newline

\section{Finalizing report}

Due by June 26, 2024.\newline

\noindent\textbf{Goal:} Thesis report is finalized by addressing any open chapters and ensuring overall coherence and completeness.\newline

\noindent\textbf{Artifacts:} Thesis document \newline

\noindent\textbf{Sprints:} 1. Weeks 26-27\newline

\section{Submission}

Due by July 14, 2024.\newline

\noindent\textbf{Goal:} Report for submission is complete and refined for submission, any remaining issues or concerns are addressed. It works as a buffer period to accommodate any unexpected delays or last-minute adjustments before submission.\newline

\noindent\textbf{Artifacts}: Final thesis submission.

\noindent\textbf{Sprints:} 1. Week 28


